\plaintitle

### 2016-04-21 Paper/paper.tex
Bugfix and minor updates

@@

\subsection{The team view}
This view as well as the statistics view should give the user the ability to search
for explanations why a team is is performing better or worse over seasons. On the 
other hand, a user can see what impact a change in team characteristics has on its
overall performance.
This view shows each player of the team on its field postions. Shirts aligned next to 
each other will thus share the same position. The size of a shirt would illustrate a
players performance on this spot. The PES score () is initiated. This view should give
a user insight on how strong or weak a particular team is for a specific field position.
A user can then scroll through time, see how field positions evolve and what the influence
is over time.
Initially we designed this view more elaborate. When the user would click on a shirt,
specific player information would be shown. Next to some general text information, 
we would have visualised a number of player statistics as small multiples. A bell curve
should have informed how a player scores compared to his team, other players in the 
league on this position or all other players in the league. We considered other charts for
the small multiples as well. A box plot or bullet was less clear for us to indicate where
a player stands compared to the group he was compared with. Alternatives for the small 
multiples were evaluated as well. One good alternative was the shooting signature.
<http://peterbeshai.com/buckets/app/#/playerView/201935_2015>
However, creating such a visualization is again a project on itself and due to time 
constraints we left it aside. Other possibilities such as a heatmap or spider web didn't
fulfill our need to give the visitor a clear overview of how a player performed compared
to its peergroup.
<Sketch of the small multiples>

@@

\subsection{Each component should be informative}
In order to have a good visualization as a whole, each component should be a clear and 
informative visualization on itself. This is a lesson learned from our work, but also when
evaluating the work of peers. We started noticing that most components in a visualization 
lack references and hence are not informative enough. Eg. each small multiple of a statisctic
in the statistics view on itself gives sufficient information to stand on itselfs. The bar in
the small multiple indicates the score in the selected season and enables the user to evaluate
that score over time. Have there been better scores, or worse scores. Is this score part of 
an upward movement during years? 
For this reason we can argue that the circle representing the teams SRS score in the statisctics
view is not the best choice. We could have chosen a bar chart with an indication of the best and
worst score for that specific team over time or for the best & worst team in that season.

\subsection{Custom visualizations]
Before exploring what is out there in the D3js world, we made our own sketches. This is how
we came up with the 3 custom views that makes our visualization. When comparing our design 
with alternatives we could not find something that satisfied our needs. Nonetheless, they gave
us inspiration to fine tune our designs. Although we are happy very happy with our result and
we are convinced it was the right choice reach our goal, it had some draw backs.
We noted that other teams had more freedom in exploring multiple different visualizations which
enabled them to evaluate different options with trial and error. A luxury we did not have. We 
could have prepared our data in a format that was more compatible with out of the box examples,
but this would have had too much of an impact on our result.
Next to that, although we've tried to write our code as general as possible, we're not convinced
this could be shared in such a way that other information visualizer could easily re-use our work
to vizualise other sports.

@@

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{sample}

>>>>

\usepackage[
    backend=biber,
    style=draft
]{biblatex}

\addbibresource{paper.bib}

@@

\subsection{The team view}
This view as well as the statistics view should give the user the ability to search
for explanations why a team is is performing better or worse over seasons. On the 
other hand, a user can see what impact a change in team characteristics has on its
overall performance.
This view shows each player of the team on its field postions. Shirts aligned next to 
each other will thus share the same position. The size of a shirt would illustrate a
players performance on this spot. The PES score () is initiated. This view should give
a user insight on how strong or weak a particular team is for a specific field position.
A user can then scroll through time, see how field positions evolve and what the influence
is over time.
Initially we designed this view more elaborate. When the user would click on a shirt,
specific player information would be shown. Next to some general text information, 
we would have visualised a number of player statistics as small multiples. A bell curve
should have informed how a player scores compared to his team, other players in the 
league on this position or all other players in the league. We considered other charts for
the small multiples as well. A box plot or bullet was less clear for us to indicate where
a player stands compared to the group he was compared with. Alternatives for the small 
multiples were evaluated as well. One good alternative was the shooting signature.\cite{peterbeshai}
However, creating such a visualization is again a project on itself and due to time 
constraints we left it aside. Other possibilities such as a heatmap or spider web didn't
fulfill our need to give the visitor a clear overview of how a player performed compared
to its peergroup.
<Sketch of the small multiples>

@@

\subsection{Each component should be informative}
In order to have a good visualization as a whole, each component should be a clear and 
informative visualization on itself. This is a lesson learned from our work, but also when
evaluating the work of peers. We started noticing that most components in a visualization 
lack references and hence are not informative enough. Eg. each small multiple of a statisctic
in the statistics view on itself gives sufficient information to stand on itselfs. The bar in
the small multiple indicates the score in the selected season and enables the user to evaluate
that score over time. Have there been better scores, or worse scores. Is this score part of 
an upward movement during years? 
For this reason we can argue that the circle representing the teams SRS score in the statisctics
view is not the best choice. We could have chosen a bar chart with an indication of the best and
worst score for that specific team over time or for the best and worst team in that season.

\subsection{Custom visualizations}
Before exploring what is out there in the D3js world, we made our own sketches. This is how
we came up with the 3 custom views that makes our visualization. When comparing our design 
with alternatives we could not find something that satisfied our needs. Nonetheless, they gave
us inspiration to fine tune our designs. Although we are happy very happy with our result and
we are convinced it was the right choice reach our goal, it had some draw backs.
We noted that other teams had more freedom in exploring multiple different visualizations which
enabled them to evaluate different options with trial and error. A luxury we did not have. We 
could have prepared our data in a format that was more compatible with out of the box examples,
but this would have had too much of an impact on our result.
Next to that, although we've tried to write our code as general as possible, we're not convinced
this could be shared in such a way that other information visualizer could easily re-use our work
to vizualise other sports.

@@

% REFERENCES FORMAT
% References must be the same font size as other body text.
%\bibliographystyle{SIGCHI-Reference-Format}
\printbibliography
